The Controlled Choice Design and Paternalism in Pawnshop Borrowing? \\ Preliminary --comments welcome

### 2023-04-20 donde.tex
changes after presentation(s)...rewriting of text

\section{Introduction}
Many people have a difficult time accumulating and retaining capital unless they are provided a structure within which to do so.  The behavioral lens on intertemporal financial services has provided critical insights on this problem, suggesting that saving from cash-in-hand is challenging \citep{Ashraf, Pascaline}, that credit may be preferred to savings as a way of accumulating capital simply because credit repayment contracts provide more structure \cite{Murdoch}, and even that the absence of structured financial contracts may be a key barrier preventing the poor from climbing out of poverty \citep{bertrand2004behavioral, collins2009portfolios}.  A large behavioral literature has illustrated that the addition of commitment-style product features improves the ability to accumulate savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters} and to retire debt \citep{Bertrand, heidhues2010exploiting}.  As a consequence, credit markets featuring limited-liability loans such as small-business financing or microfinance typically take a highly structured approach to credit contracts with frequent repayments and reminders as a way of inducing repayment.  As pointed out by \cite{Laibson2018}, because many of these forms of commitment may be desirable to principals but not demanded by agents (or by the right agents), these mechanisms are often ‘shrouded’, meaning that commitment is embedded in products in ways that are not advertised to clients as such.

In this paper we examine pawn contracts, an understudied form of credit despite their relative ubiquity \citep{carter2012pawnshops}, and a major vehicle through which poor households may dis-accumulate savings.  There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.  In China it is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner, a Mexican pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.  Pawnshop lending presents an inverted lending case:  since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.  Our collaborating lender gave only 70\% of the value of the pawn in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due.  This combination of features means that the lender makes 90\% more profit over three months for a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).  While an older literature considers the exploitative potential in over-collateralization and underpricing of collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.  When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments that represent the opposite of what the behavioral literature tells us will induce repayment. To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment to induce default in a manner not obvious to borrowers.  Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.

Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of commitment in pawn repayment contracts.  Our control arm illustrates the costs of the status quo contract; fully 57\% of borrowers default and so lose their pawn.  We then implement a `commitment choice’ arm, in which borrowers are able at the time of taking a loan to opt in to a structured repayment contract, in which they are asked to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, and borrowers levied a nominal fee of 2\% of that month's payment in case of delinquency as a reminder/reinforcement of the importance of these interim payments.  In addition, we include a `forced commitment’ arm, in which all borrowers are required to repay using the commitment structure.  The combination of voluntary and forced commitment in the same study allows us to address several key questions.  First, does using more structured repayment contracts help pawnshop borrowers to achieve higher repayment rates, thereby saving them money?  Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers to meaningfully change repayment behavior?  Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the treatment on compliers and the treatment on non-compliers by comparison across the control, choice, and forced arms.

Our results suggest that the structure of the commitment is strongly effective in preventing default, with the average individual in the forced arm paying financing costs inclusive of fees that are 9.4\% lower than the control (from \$3157 to \$2860 MXN), while the likelihood of recovering their pawn increases by 26\% (from 43\% to 55\%).  Results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, suggesting that in the context of a commitment structure it is possible to save borrowers money by charging them fees!  Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, and those most overconfident about their probability of repayment, experience larger gains.\footnote{As in \cite{Rabin2018} we contrast subjects' \textit{own predictions} of their behavior with their actual behavior, but we do it in a natural setting.}  Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. That is, the commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster, making them more likely to recover their pawn at a lower financial cost.

Borrowers assigned to the forced commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.  However, when offered the choice of commitment, very few borrowers elect to commit voluntarily.  Only 10\% of the choice arm takes up the contract, and none of the core study outcomes are significantly improved by the ability to choose commitment.

@@

Most importantly, our multi-arm design allows us to show that the \textit{wrong} people choose commitment when offered it.   We illustrate this point in three distinct ways.  First, we use a Random Forest algorithm \citep{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.  93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.  Second, a Boosted Classification Algorithm arrives at a similar answer, showing that the borrowers naturally cluster into two groups, one of which is likely to choose commitment and does not benefit from it, and the other the reverse.  Finally, estimating LATEs on compliers and non-compliers alike we show that the estimated treatment effect on non-compliers is larger than the treatment effect on compliers.  That is, those choosing commitment benefit less from commitment than those not choosing it.  Hence our results show clearly that a paternalistic policy forcing borrowers into a more rigid and structured repayment regimen is uniquely beneficial to them.  While this perverse relationship between choice and benefits from commitment echo closely the findings of \cite{Sprenger} we are the first to be able to examine this relationship using a high-stakes, money-metric outcome in a natural field environment.

Additional evidence of the importance of paternalism in pawnshop commitment is provided by two additional study arms offering variants of `soft' commitment.  In one arm all borrowers were asked to commit to make three monthly payments instead of a single balloon payment, but no external reminders or fees were imposed.  In a second arm borrowers were given the ability to choose whether to engage in this form of soft commitment.  Both of these arms are completely ineffective, suggesting that it is the combination of external imposition of the contract along with the teeth provided by the reminder and fees that generate the savings to borrowers relative to the status quo contract.

What explains the persistence of a contract so contrary to borrowers’ interests?  First, we show substantial levels of over-optimism among borrowers.  Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.  While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it and subsequently default \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.  Finally, while we are working with a lender who has a social mission and is interested in understanding how to help borrowers, there is no free lunch.  The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.

Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates.  By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate; we estimate that over 50\% of the borrowers in our study are naïve hyperbolics in the sense that they would benefit from commitment but will not choose it.  While our results are driven by the intersection of overcollateralization and a potential selection of the borrower pool towards myopia and short-term financial thinking, these attributes are likely to be present in many types of pro-poor financial markets where individuals lack the credit histories to be able to leverage short-term credit without collateral.  This suggests that regulators of such markets would do well to consider the broader financial costs of lending products, including what is paid through equilibrium default, and to consider imposing more structured lending products that tilt the scales towards allowing borrowers to repay.  While commitment-style repayment contracts decrease effective liquidity by requiring faster repayment of a given loan, the improvement in expected borrower returns are so substantial as to prove welfare improving at all but the most astronomical discount rates.

These conclusions speak to several strands of the literature.  First, they suggest consequential ways in which different financial services draw client pools with distinct behavioral biases.  While research in microfinance markets has not found the same benefits from providing a more regularized repayment environment \citep{Pande}, those experiments are performed over the top of highly structured contracts and among borrower pools who may have selected into that type of lending precisely because it provides structure.  Second, we broaden the analysis of the extent to which voluntary commitment mechanisms are desirable.  Like our study, commitment demand has been found to be low in a number of contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), and by illustrating a mechanism for the failure of self-commitment (over-optimism) we may help contextualize those studies in which demand has been found to be more robust (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). Finally, we provide only the second case in the literature, and the first in the analysis of financial products, to illustrate the perverse result that those who opt into commitment are precisely the individuals who do not need it \citep{Sprenger}.

@@

\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the designed of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.  It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers. The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments. The propose of the small fee was to mainly to make the structured schedule salient, not to be a large disincentive to be late. Transportation cost to go to the branch to pay is on the same order of magnitude as the fee in average.\footnote{The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. In contrast with \cite{John} we don't let the clients choose the size of the fee. \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment. %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
} To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose. The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimate a battery of treatment effects above an average treatment effect under fairly mild assumptions.

@@

\paragraph{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey we implemented. The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece. In particular, the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn. Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed. After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.  We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended. Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm. The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawns.

@@

We start by estimating average treatment effects for those assigned to the Forced commitment and the Choice arms, compared to those assigned to the Control group. As we explain below, only about \hl{XXX\%} of those in the choice arm chose the monthly payment option.

@@

>>>>

\section{Introduction}

Restrictions of choice are often surreptitiously imposed on consumers. Firms limit their worker's freedom by requiring time-consuming progress reports,  schools impose deadlines and pop quizzes, and loan contracts often require monthly repayment. As pointed out by \cite{Laibson2018}, although these choice-restricting mechanisms may be beneficial to firms and clients, they are often disliked by the latter, and therefore ‘shrouded’ by firms, i.e. not advertised but nonetheless embedded in products. \cite{Laibson2018} coins the term ``private paternalism'' for cases when restrictions on the freedom of choice is implemented by a firm in a way that advances a client's interests.

Although the examples above are plausible, substantiating a case for private paternalism is not easy. It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose on that characteristic. This is not an easy task because a given person wither has or does not have choice, and because choice induces selection, potentially biasing causal estimates. A large behavioral literature has illustrated that allocating borrowers to a commitment-savings product increase savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature does not show that commitment would not be chosen by those that would benefit from it, that is, that the Treatment Effect on the Untreated (TuT) is positive. In fact, selection on gains has such wide acceptance that economists often impose it in their models \hl{CITES}. In microfinance, a context close to ours, \citep{Murdoch} claim that there exists positive selection, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments. However, they are unable to show that borrowers indeed benefit or that they indeed positively select based on treatment effects.

%Many people have a difficult time accumulating and retaining capital unless they are provided a structure within which to do so.  The behavioral lens on intertemporal financial services has provided critical insights on this problem, suggesting that saving from cash-in-hand is challenging \citep{Ashraf, Pascaline}, that credit may be preferred to savings as a way of accumulating capital simply because credit repayment contracts provide more structure \cite{Murdoch}, and even that the absence of structured financial contracts may be a key barrier preventing the poor from climbing out of poverty \citep{bertrand2004behavioral, collins2009portfolios}.  A large behavioral literature has illustrated that the addition of commitment-style product features improves the ability to accumulate savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters} and to retire debt \citep{Bertrand, heidhues2010exploiting}.  As a consequence, credit markets featuring limited-liability loans such as small-business financing or microfinance typically take a highly structured approach to credit contracts with frequent repayments and reminders as a way of inducing repayment.  As pointed out by \cite{Laibson2018}, because many of these forms of commitment may be desirable to principals but not demanded by agents (or by the right agents), these mechanisms are often ‘shrouded’, meaning that commitment is embedded in products in ways that are not advertised to clients as such.

This paper studies the benefits of restricting choice in the context of pawnbroker lending. Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a 43 billion dollar industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.

Our collaborating pawn lender (henceforth Lender P) gave 70\% of the value of the pawn in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due at no penalty. This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months for a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid). While an older literature considers the exploitative potential in over-collateralization and underpricing of collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.  %When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments. 
To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment features to induce default in a manner not obvious to borrowers. Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.

%clients lose their pawn, and among those that recover it almost all of them pay in the last days, just before the loan elapses.\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}

%In this paper we examine pawn contracts, an understudied form of credit despite their relative ubiquity \citep{carter2012pawnshops}, and a major vehicle through which poor households may dis-accumulate savings.  There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.  In China it is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner, a Mexican pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.

Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of payment structure in pawn repayment contracts. Our control arm illustrates the costs of the status quo contract; fully 57\% of borrowers default and so lose their pawn.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a `commitment choice’ arm, in which borrowers are able at the time of taking a loan to opt in to a structured repayment contract, in which they are asked to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, and borrowers levied a nominal fee of 2\% of that month's payment in case of delinquency as a reminder/reinforcement of the importance of these interim payments. In addition, we include a `forced commitment’ arm, in which all borrowers are required to repay using the monthly payment structure.

The combination of voluntary and forced commitment within the RCT allows us to address several key questions.  First, does using more structured repayment contracts help pawnshop borrowers to save on financing cost. Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?  Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the Treatment on the Treated (ToT) and the Treatment on the Untreated (TuT), using the control, choice, and forced arms.

Our results suggest that the structure of the commitment is strongly effective in preventing default, with the average individual in the forced arm paying financing costs inclusive of fees that are \hl{20\%} lower than the control, while default decreases by 6.5 percentage points (15\% of the mean). In terms of Annual Percentage Rates, the financial cost of borrowing is reduced by 34 percentage points. That is, imposing commitment structure it is possible to save borrowers money by charging them fees! These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using the subjective instead of the gold value of the pawn, and imputing some adjustment for liquidity lost by requiring monthly payments.

The monthly payment contract seems to be achieving these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not, saving the later payments towards recovery. In the treatment group, the first payment occurs 13 days earlier, the fraction recovering on the first visit by is 7.9 percentage point higher. Commitment contract decreases fraction of borrowers making a payment and not recovering by 7 percentage points. \hl{Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. That is, the commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster, making them more likely to recover their pawn at a lower financial cost.}

In spite of a large average treatment effect documenting financial cost savings, given the opportunity in the choice arm, only 11\% of borrowers actually choose commitment. If the effect of commitment were homogeneous, this would be enough to conclude that the 89\%
who did not choose it would have been financially better off if they had. However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}. Can the borrowers who did not choose commitment be those who simply don’t need it? We address this question by sequentially imposing more structure in the problem.

\hl{We start by bounding the distribution of treatment effects $Y_{1i}-Y_{0i}$ using the two marginal distribution } in the treatment and control arms as in \cite{fan2010sharp}. We find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand even though the treatment effect would be positive for them. Then, we impose the mild exclusion restriction that the effect of the contract does not depend on how they got it, that is: choosing a contract has the same treatment effect as being assigned to the contract.\footnote{This is a frequently used assumption even if often implicit. For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.} We show that in this case our 3-armed experiment point identifies the TuT. We then estimate that the financial cost savings of the TuT is large, at \$356 pesos, equivalent to 24 percentage point savings in APR. That is, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{We estimate a positive ToT that is larger than the TuT, but it is imprecise\footnote{This results from the smaller sample size, given that few chose the monthly payment contract.}, and the hypothesis of ToT=TuT is rejeted only with 13 percent confidence for the APR and 12 percent confidence for default.}  We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e. the average selection bias is negative). Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that \hl{70\%} of would-be non-choosers would save on financial cost by being assigned to frequent payments. That is, the benefits of imposing a monthly payment are distributed broadly. \hl{TuT benefits are particularly large for XXX CHARACTERISTICS, and ToT benefits for those with XXX.}

\textcolor{brown}{In a final step, we use the Causal Random Forest algorithm of \cite{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.  93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.} \textcolor{blue}{Targeting frequent payment products to those that benefit the most is a policy that should be explored. In this context we calculate \hl{XXX}.}

%however those most economically vulnerable, and those most overconfident about their probability of repayment, experience larger gains.

%\footnote{As in \cite{Rabin2018} we contrast subjects' \textit{own predictions} of their behavior with their actual behavior, but we do it in a natural setting.}

%Borrowers assigned to the forced commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.  However, when offered the choice of commitment, very few borrowers elect to commit voluntarily.  Only 10\% of the choice arm takes up the contract, and none of the core study outcomes are significantly improved by the ability to choose commitment.

@@

%Most importantly, our multi-arm design allows us to show that the \textit{wrong} people choose commitment when offered it.   We illustrate this point in three distinct ways.  First, we use a Random Forest algorithm \citep{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.  93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.  Second, a Boosted Classification Algorithm arrives at a similar answer, showing that the borrowers naturally cluster into two groups, one of which is likely to choose commitment and does not benefit from it, and the other the reverse.  Finally, estimating LATEs on compliers and non-compliers alike we show that the estimated treatment effect on non-compliers is larger than the treatment effect on compliers.  That is, those choosing commitment benefit less from commitment than those not choosing it.  Hence our results show clearly that a paternalistic policy forcing borrowers into a more rigid and structured repayment regimen is uniquely beneficial to them.  While this perverse relationship between choice and benefits from commitment echo closely the findings of \cite{Sprenger} we are the first to be able to examine this relationship using a high-stakes, money-metric outcome in a natural field environment.

What explains the persistence of a contract so contrary to borrowers’ interests?  First, we show substantial levels of over-optimism among borrowers.  Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.\footnote{More generally \hl{demand for commitment is higher among those with XXX characteristics.}}  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico. The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.

Does learning eventually overcome the low demand for commitment? For learning to happen clients would need to experiment the frequent payment contract, and this was not the typical contract in the industry. But even if the contract was experienced, borrower may fail to learn or learn only slowly. We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat costumers than those assigned to the status-quo contract. One way to interpret this is that that having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they want to borrow more.\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one. This second explanation is unlikely since borrowers obtain a second loan not within the first 90 days of the first loan when payments are due; moreover, the correlation is also present conditional on having paid down the first loan. Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.} However, a stronger test of liking the monthly payment contract is whether conditional on coming again, they would choose frequent payments. We test this and we cannot reject that demand is not higher after experiencing the monthly payment contract, however sample sizes are small and \hl{the minimum detectable effect is XXX.}

%While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it and subsequently default \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.  Finally, while we are working with a lender who has a social mission and is interested in understanding how to help borrowers, there is no free lunch.  The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.

Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates. By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate. We hesitate to give precise policy recommendations since we don't have good measures of welfare. Even though the monthly payment contract dramatically reduces financial cost, it could potentially generate lower (or higher) anxiety. Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate. \hl{Note also that since the fee for skipping payment is 2\%, the iliquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.

%we estimate that over 50\% of the borrowers in our study are naïve hyperbolics in the sense that they would benefit from commitment but will not choose it.  While our results are driven by the intersection of overcollateralization and a potential selection of the borrower pool towards myopia and short-term financial thinking, these attributes are likely to be present in many types of pro-poor financial markets where individuals lack the credit histories to be able to leverage short-term credit without collateral. This suggests that regulators of such markets should include what is paid through equilibrium default as part of the financing cost (not done now), and to consider imposing structured lending products that tilt the scales towards allowing borrowers to repay.  While commitment-style repayment contracts decrease effective liquidity by requiring faster repayment of a given loan, the improvement in expected borrower returns are so substantial as to prove welfare improving at all but the most astronomical discount rates.

Our paper speaks to several strands of the literature.   %First, they suggest consequential ways in which different financial services draw client pools with distinct behavioral biases. 
First, to research in microfinance studying the effect of payment frequency.  While research in microfinance markets has not found the same benefits from providing a more regularized repayment environment \citep{Pande}, those experiments are performed on top of highly structured contracts and among borrower pools who may have selected into that type of lending precisely because it provides structure. This may explain why there is almost no default in the control group in \citep{Pande}. Second, we broaden the analysis of the extent to which voluntary commitment mechanisms are taken up and effective.  Like our study, commitment demand has been found to be low in a number of contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}). Other papers have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}). But unlike all these papers we can point identify the benefit the non-takers would have had if they had taken up and the benefit for the takers, and thus can talk more rigorously about private paternalism in this context.

%Finally, we provide only the second case in the literature, and the first in the analysis of financial products, to illustrate the perverse result that those who opt into commitment are precisely the individuals who do not need it \citep{Sprenger}.

Two recent papers that shed some light into private paternalism. In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies, and then find that demand for commitment is negatively correlated with such inconsistency. In the context of school choice, \cite{Walters} finds that students that select into more effective schools have smaller treatment effects from attending than those that select out. Besides being very different contexts from ours, we rely on very different methods. In contrast to \cite{Sprenger} we will directly point identify the TuT, obviating the need for elicitation of preferences to test for negative selection. In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument. \hl{FRANK, can I say something more precise than ``a structural model''?}

Methodologically we contribute to the large literature on treatment effect heterogeneity by showing how an experimental design with two forcing arms and one choice arm allows for identification of the ToT, the TuT and other important parameters under minimal assumptions. \cite{aronow2013beyond} and \cite{angrist2013extrapolate} assume no selection on gains to estimate \hl{XXX}. \cite{Walters} achieve identification of the TuT by using parametric model and a distance instrument, which requires the model to be correct and the instrument to be valid. TUT and ATE implied by LATE-and-re-weight differ sharply from his model-based estimates. The method of 
\cite{heckman2007econometric} and \cite{cornelissen2018benefits} require the availability of instrumental variable with rich support, and separability of observed and unobserved determinants of treatment effects.

@@

\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the designed of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.  It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers. The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.  The idea that the fee itself is not driving the treatment is reinforced later in the paper where we show financial benefits many times larger than the fee, as well as treatment effects even on those who would fail to recover pawns and hence not pay the fee. Transportation cost to go to the branch to pay is on the same order of magnitude as the fee on average.\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. 
In contrast with \cite{John} we don't let the clients choose the size of the fee. \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment. %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
} To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose. The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimate a battery of treatment effects above an average treatment effect under fairly mild assumptions.

@@

\paragraph{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey we implemented. The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece. These transactions include the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn. Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed. After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.  We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended. Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm. The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawns.

@@

We begin by estimating average treatment effects of assignment to the Forced commitment and the Choice arms, relative to those assigned to the Control arm. As we explain below, only about \hl{XXX\%} of those in the choice arm chose the monthly payment option.

@@

\subsubsection{Bounding the Distribution of Individual Treatment Effects}
